Combining information from photometric and spectroscopic data:\\ propogating uncertainties in spectrophotometric calibration

### 2015-05-06 tex/ms.tex
real obs param file, homogenize burn-in sequnces, fixes for non-george GP plotting

% ---- Charlie (emulateapj) mode ----
 \documentclass[iop,numberedappendix]{emulateapj}
 \usepackage{apjfonts}
% ----
\usepackage{color, hyperref}
\bibliographystyle{apj}
\input{vc}

@@

\subsection{Star Cluster Model}
\label{sec:cluster_model}
We model the stellar cluster as a single age SSP. The spectrum of a
star cluster under this assumption is given by a vector
\begin{eqnarray} \label{eq:StarModel}\displaystyle
f_{\theta_s}(\lambda_o) & = &
\frac{m_*}{4\pi d_L^2(1+z)} \, L(\sigma_*, z) \, s(\lambda, t, Z , \beta) \, e^ {-k_\lambda\tau_V} \\
\nonumber \\ 
\lambda_o & = & (1+z)\,\lambda 
\\
\theta_s & \equiv & \left[ m_*, t, Z, \tau_V, z, d_L, \sigma_*, \beta \right]
\quad ,
\end{eqnarray} where the
parameters $\theta_s$ include 
the stellar mass $m_*$, 
effective optical depth to dust in the $V$-band $\tau_V$, 
luminosity distance $d_L$,
and redshift $z$.
The matrix $L(\sigma_*, z)$ is a convolution kernel representing the
stellar velocity profile,
and $\sigma_*$ is the stellar velocity dispersion. 
The shape of the dust attenuation curve is given by $k_\lambda \equiv
\tau_\lambda/\tau_V$.  
The observed frame wavelengths $\lambda_o$ are related to the
restframe wavelengths $\lambda$ in the usual way.

@@

\item Mock perfectly calibrated data: inference using spectroscopy and one
  photometric band, assuming no calibration uncertainty.  This is as
  good as we could get given the data and its uncertainties.

\item Mock perfectly calibrated data: inference using spectroscopy and one
  photometric band, with the full calibration model.  This is how much
  including additional calibration flexibility hurts the posterior
  PDFs compared to perfectly known calibration.

\item Mock uncalibrated data:  inference using spectroscopy and one
  photometric band, with full calibration model.  This is how well we
  can get the calibration \emph{and} the physical parameters with
  spectroscopy only.

\item Mock data: inference using photometry only.  This is how well we
  can get the physical parameters using photometry only.

\item Mock uncalibrated data: inference using spectroscopy and all
  photometry, full calibration model.  This is how well we
  can get the calibration and physical parameters using spectroscopy
  and photometry.

>>>>

% ---- Charlie (emulateapj) mode ----
 \documentclass[iop,numberedappendix]{emulateapj}
 \usepackage{apjfonts}
% ----
\usepackage{color, hyperref}
\usepackage[normalem]{ulem}
\bibliographystyle{apj}
\input{vc}

@@

\subsection{Star Cluster Model}
\label{sec:cluster_model}
We model the stellar cluster as a single age SSP. The spectrum of a
star cluster under this assumption is given by a vector
\begin{eqnarray} \label{eq:StarModel}\displaystyle
f_{\theta_s}(\lambda_o) & = &
L(\sigma_s, z) ,\, \frac{m_*}{4\pi d_L^2(1+z)} \, s(\lambda, t, Z , \beta) \, e^ {-k_\lambda\tau_V} \\
\nonumber \\ 
\lambda_o & = & (1+z)\,\lambda 
\\
\theta_s & \equiv & \left[ m_*, t, Z, \tau_V, z, d_L, \sigma_*, \beta \right]
\quad ,
\end{eqnarray} where the
parameters $\theta_s$ include 
the stellar mass $m_*$, 
effective optical depth to dust in the $V$-band $\tau_V$, 
luminosity distance $d_L$,
and redshift $z$.
The matrix $L(\sigma_s, z)$ is a convolution kernel representing the
stellar velocity profile,
and $\sigma_s$ is the stellar velocity dispersion. 
The shape of the dust attenuation curve is given by $k_\lambda \equiv
\tau_\lambda/\tau_V$.  
The observed frame wavelengths $\lambda_o$ are related to the
restframe wavelengths $\lambda$ in the usual way.

@@

\item \sout{Mock perfectly calibrated data: inference using spectroscopy and one
  photometric band, assuming no calibration uncertainty.  This is as
  good as we could get given the data and its uncertainties.}

\item \sout{Mock perfectly calibrated data: inference using spectroscopy and one
  photometric band, with the full calibration model.  This is how much
  including additional calibration flexibility hurts the posterior
  PDFs compared to perfectly known calibration.}

\item \sout{Mock uncalibrated data:  inference using spectroscopy and one
  photometric band, with full calibration model.  This is how well we
  can get the calibration \emph{and} the physical parameters with
  spectroscopy only.}

\item \sout{Mock data: inference using photometry only.  This is how well we
  can get the physical parameters using photometry only.}

\item \sout{Mock uncalibrated data: inference using spectroscopy and all
  photometry, full calibration model.  This is how well we
  can get the calibration and physical parameters using spectroscopy
  and photometry.}
